---
name: Rob J Hyndman
address: "Department of Econometrics & Business Statistics,\\tabularnewline Monash University, VIC 3800, Australia."
www: robjhyndman.com
email: "Rob.Hyndman@monash.edu"
github: robjhyndman
date: "`r format(Sys.Date(), '%B %Y')`"
date-format: "MMMM YYYY"
position: FAA, FASSA, BSc (Hons), PhD, AStat
format: cv-pdf
pdf-engine: latexmk
header-includes:
  - \geometry{left=1.5cm,right=1.5cm,top=1.8cm,bottom=1.7cm}
  - \definecolor{headcolor}{HTML}{000088}
---

\titlespacing{\section}{0pt}{1.ex}{0.5ex}
\fontsize{10}{11.5}\sf
\thispagestyle{empty}
\enlargethispage*{0.5cm}

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = FALSE
)
library(dplyr)
library(RefManageR)
source("R/add_bib_section.R")
source("R/pretty.R")

# Remove any temporary bib file
if (fs::file_exists("temp.bib")) {
  fs::file_delete("temp.bib")
}

targets::tar_load(c(pubs, rjh, rjhcites))
```

# Current position

```{r employment, results='asis'}
tribble(
  ~Years, ~Position,
  "2003--", "\\textbf{Professor}, Department of Econometrics \\& Business Statistics, Monash University"
) %>%
  baretable()
```

# Fellowships

  * Fellow of the Australian Academy of Science (elected 2021).
  * Fellow of the Academy of the Social Sciences in Australia (elected 2020).
  * Fellow of the International Institute of Forecasters (elected 2021).

# Selected awards and honours

```{r awards, results='asis'}
awards <- tribble(
  ~Year, ~Award,
  2021, "Pitman Medal, Statistical Society of Australia",
  2007, "Moran Medal for Statistical Science, Australian Academy of Science"
) %>%
  baretable()
```

# Selected books

```{r books}
#| output: asis
pubs[c("fpp3", "expsmooth08")] |>
  add_bib_section(show_cites = TRUE, rjhcites=rjhcites)
```

\vspace*{-0.2cm}

# Selected papers

```{r}
# Count papers
npapers <- pubs %>%
  as_tibble() |>
  filter(!(type %in% c("book", "thesis", "review"))) %>%
  NROW()
```

Since 1991 I have authored `r npapers` research papers or book chapters on statistical topics. Some highlights are listed below, with citations taken from Google Scholar on `r format(Sys.time(), "%e %B %Y")`.  My h-index is `r rjh$All[2]` with total citations of `r prettyNum(rjh$All[1], big.mark=",")`.


```{r bibfile}
#| output: asis
pubs[c(
    "tsibble", "globalforecasting", "fforma",
    "smartmeterhts", "mint", "HF10", "DHS11", "hierarchical",
    "VHNC10", "HK06", "HK08", "HKSG02", "HF96", "m3pca",
    "HU07", "HDR96", "HB08"
  )] |>
  add_bib_section(show_cites = TRUE, rjhcites=rjhcites)
```
