---
name: Rob J Hyndman
address: "Department of Econometrics & Business Statistics,\\tabularnewline Monash University, VIC 3800, Australia."
www: robjhyndman.com
phone: +61 3 9905 5141
email: "Rob.Hyndman@monash.edu"
twitter: robjhyndman
github: robjhyndman
date: "`r format(Sys.Date(), '%B %Y')`"
date-format: "MMMM YYYY"
position: FAA, FASSA, BSc (Hons), PhD, AStat
bibliography: [rjhreports.bib]
format: cv-pdf
header-includes:
  \definecolor{headcolor}{HTML}{000088}
---

\newcounter{bib}

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = FALSE
)
library(dplyr)
library(RefManageR)
source("R/add_bib_section.R")
source("R/pretty.R")

# Remove any temporary bib file
if (fs::file_exists("temp.bib")) {
  fs::file_delete("temp.bib")
}

targets::tar_load(c(pubs, reports, packages, grants, rjh_packages, rjh, rpackages_bib))
```

# Education and qualifications

```{r degrees, results='asis'}
tribble(
  ~Degree, ~Institution, ~Year,
  "B.Sc.(Hons)", "University of Melbourne", 1988,
  "Ph.D.", "University of Melbourne", 1992,
  "A.Stat.", "Statistical Society of Australia", 2000
) |>
  baretable()
```

# Fellowships

  * Fellow of the Australian Academy of Science (elected 2021).
  * Fellow of the Academy of the Social Sciences in Australia (elected 2020).
  * Fellow of the International Institute of Forecasters (elected 2021).

# Employment history

```{r employment, results='asis'}
tribble(
  ~Start, ~End, ~Position,
  1985, 1992, "\\textbf{Statistical consultant}, Department of Statistics, University of Melbourne",
  1993, 1994, "\\textbf{Lecturer}, Department of Statistics, University of Melbourne",
  1995, 1996, "\\textbf{Lecturer}, Department of Mathematics and Statistics, Monash University",
  1997, 1998, "\\textbf{Senior Lecturer}, Department of Mathematics and Statistics, Monash University",
  1998, 1998, "\\textbf{Visiting Professor}, Department of Statistics, Colorado State University",
  1998, 2000, "\\textbf{Senior Lecturer}, Department of Econometrics \\& Business Statistics, Monash University",
  2001, 2003, "\\textbf{Associate Professor}, Department of Econometrics \\& Business Statistics, Monash University",
  2002, 2002, "\\textbf{Visiting Senior Research Fellow}, Mathematical Sciences Institute, Australian National University",
  2003, NA, "\\textbf{Professor}, Department of Econometrics \\& Business Statistics, Monash University",
  2016, 2016, "\\textbf{KNAW Visiting Professor}, TU/Eindhoven, Netherlands",
) |>
  arrange(-Start) |>
  mutate(
    Start = as.character(Start),
    End = as.character(End),
    End = tidyr::replace_na(End, ""),
    Years = if_else(End == Start,
      as.character(Start),
      paste(Start, "--", End, sep = ""),
      paste(Start, "--", End, sep = "")
    )
  ) |>
  select(Years, Position) |>
  baretable()
```

# Academic and research leadership

  * **Head**, Department of Econometrics & Business Statistics, Monash University. 2019--2022.
  * **Director**, Business & Economic Forecasting Unit, Monash University. 2001--2017.
  * **Director of Consulting**, Econometrics and Business Statistics, Monash University. 2000--2014.
  * **Director**, Monash University Statistical Consulting Service, 1997--1998.
  * **Director**, Key Centre for Statistical Science, 1996--1998.

# Awards and honours

```{r awards, results='asis'}
tribble(
  ~Year, ~Award,
  2022, "Australian Awards for University Teaching citation for outstanding contributions to student learning",
  2021, "Pitman Medal, Statistical Society of Australia",
  2021, "Vice-Chancellor's Award for Innovation in Learning and Teaching",
  # 2020, "MSA Teaching Excellence Award for Business and Economics, Monash Student Association",
  2020, "Dean's Award for Innovation in Learning and Teaching, Monash Business School",
  2018, "Commendation for the Dean's Award for Research Impact, Monash Business School",
  2014, "Nominee for MPA Supervisor of the Year, Monash Postgraduate Association",
  2010, "Dean's Award for Excellence in Innovation and External Collaboration, Monash Business School",
  2010, "HP Innovation Research Award",
  2008, "Dean's Award for Excellence in Research, Monash Business School",
  2008, "Vice-Chancellor's Award for Postgraduate Supervisor of the Year, Monash University",
  2007, "Moran Medal for Statistical Science, Australian Academy of Science",
  1998, "Award for excellence in teaching, Monash Science Society",
  1990, "Finalist, Channel Ten Young Achiever Awards",
  1988, "Dwights Prize in Statistics, University of Melbourne",
  1987, "Norma McArthur Prize in Statistics, University of Melbourne",
  1986, "Second Maurice H Belz Prize in Statistics, University of Melbourne"
) |>
  filter(!grepl("HP Innovation", Award)) |>
  baretable()
```

# Editorial boards

```{r positions, results='asis'}
tribble(
  ~Start, ~End, ~Position,
  2023, NA, "\\textbf{Executive Editor}, \\textit{The R Journal}",
  2011, NA, "\\textbf{Editor}, \\textit{Journal of Statistical Software}",
  2019, NA, "\\textbf{Associate Editor}, \\textit{International Journal of Forecasting}",
  2005, 2018, "\\textbf{Editor-in-Chief}, \\textit{International Journal of Forecasting}",
  2001, 2004, "\\textbf{Associate Editor}, \\textit{International Journal of Forecasting}",
  2001, 2004, "\\textbf{Theory and Methods Editor}, \\emph{Australian \\& New Zealand Journal of Statistics}",
) |>
  mutate(
    Start = as.character(Start),
    End = as.character(End),
    End = tidyr::replace_na(End, ""),
    Year = paste(Start, "--", End, sep = "")
  ) |>
  arrange(desc(Start)) |>
  select(Year, Position) |>
  baretable()
```

\newpage

# Society memberships

  * Fellow, International Institute of Forecasters
  * Elected Member, International Statistical Institute
  * Member, International Association for Statistical Computing
  * Member, International Society for Business and Industrial Statistics
  * Member, Statistical Society of Australia

# Society leadership

  * Director, International Institute of Forecasters, 2005--2018.
  * Member, Scientific Program Advisory Group, Statistical Society of Australia, 2001--2004
  * Central Council member, Statistical Society of Australia, 1993--1996.
  * Secretary, Victorian branch, Statistical Society of Australia, 1993--1995.

# Research

  * Since 1991 I have authored `r NROW(pubs)` papers, chapters or books on statistical topics (listed on pages \pageref{papersstart}--\pageref{papersend}).
  * On Google Scholar my h-index is `r rjh$All[2]` with total citations of `r prettyNum(rjh$All[1], big.mark=",")` (as at `r format(Sys.time(), "%e %B %Y")`).
  * My current research involves the analysis of large collections of time series, and includes visualization, forecasting, reconciliation, modelling and anomaly detection..
  * I currently supervise 6 PhD students. I have supervised to completion 30 PhD students and 3 Masters students.
  * I have been a PhD examiner more than 15 times for students in Europe, Australia and Asia.
  * I publish the [*Hyndsight*](https://robjhyndman.com/hyndsight) blog on research issues which receives an average of about 1500 pageviews per day.
  * I have coauthored `r NROW(packages)` R packages as a result of my research (listed on pages \pageref{packagestart}--\pageref{packageend}). There have been over `r round(sum(rjh_packages$downloads, na.rm=TRUE)/1e6)` million downloads of my packages since 2015 (to `r format(Sys.time(), "%e %B %Y")`).

# Public lectures

  * ANU public lecture, *Forecasting the future and the future of forecasting*, Canberra, Nov 2022.
  * Cornish lecture, *Feasts and fables: modern tools for time series analysis*, Adelaide, Nov 2021.
  * ACEMS public lecture, *Uncertain futures: what can we forecast and when should we give up?*, Aug 2021.
  * Monash master class, *Forecasting the future of the power industry: What can you learn from smart meter data?*, Melbourne, Sep 2018.
  * Yahoo Big Thinkers lecture, *Exploring the boundaries of predictability: what can we forecast, and when should we give up?*, California, Jun 2015.
  * Invited speaker, *Forecasting functional time series*, Australian Frontiers of Science, Canberra, Feb 2008.
  * Knibbs lecture, *Population forecasting and the importance of being uncertain*, Statistical Society of Australia, Canberra, Nov 2007.
  * Belz lecture, *Forecasting and the importance of being uncertain*, Statistical Society of Australia, Melbourne, Oct 2006.

# Major presentations

  * Suessmilch Lecturer, *vital: Tidy data analysis for demography using R*, Max Planck Institute for Demographic Research, Rostock, Jun 2024.
  * Keynote speaker, *Forecasting the future and the future of forecasting*, 2024 Australian Treasuries Forecasting Conference, Feb 2024.
  * IIF Distinguished Lecturer, *Forecast reconciliation*, online series of lectures, Nov 2023.
  * Keynote speaker, *Visualization of complex seasonal patterns in time series*, 800 year anniversary, University of Padua, Sep 2022.
  * Keynote speaker, *Creating social good for forecasters*, Forecasting for Social Good workshop, Oxford UK, Jul 2022.
  * Blakers lecture, *Forecasting the future and the future of forecasting*, ANU-AAMT National Mathematics Summer School, Jan 2022.
  * Keynote speaker, *Ten years of forecast reconciliation*, International Symposium on Forecasting, online, Oct 2020.
  * Workshop leader, *Tidy time series and forecasting in R*, rstudio::conf, San Francisco, Jan 2020.
  * ISI short course, *High-dimensional time series analysis*, Kuala Lumpur, Aug 2019.
  * Workshop leader, *Forecasting: principles and practice*, New York City, Jun 2018.
  * Keynote speaker, Beijing Workshop on Forecasting, Nov 2017.
  * Keynote speaker, ICML Time Series Workshop, Sydney, Aug 2017.
  * Invited speaker, International Symposium on Energy Analytics, Cairns, Jun 2017.
  * Keynote speaker, *Forecasting large collections of related time series*, German Statistical Week, Augsburg, Sep 2016.
  * Keynote speaker, *Forecasting big time series data using R*, Chinese R conference, Nanchang, Oct 2015.
  * Invited speaker, *Visualization and forecasting of big time series data*, ACEMS Big data workshop, QUT, Feb 2015.
  * Workshop leader, *Forecasting: principles and practice*, University of Western Australia, Sep 2014.
  * Workshop leader, *Functional time series in demography*, Humboldt University, Berlin, Jun 2014.
  * Keynote speaker, *Challenges in forecasting peak electricity demand*, Energy Forum, Valais, Switzerland, Jun 2014.
  * Workshop leader, *State space models for time series*, Australian Bureau of Statistics, May 2014.
  * Keynote speaker, *Automatic time series forecasting*, "New Trends on Intelligent Systems and Soft Computing 2014", University of Granada, Spain, Feb 2014.
  * Keynote speaker, *Forecasting without forecasters*, International Symposium on Forecasting, Seoul, Jun 2013.
  * Keynote speaker, *Man vs Wild Data*, Young Statisticians Conference, Melbourne, Feb 2013.
  * Invited speaker, *Advances in automatic time series forecasting*, Australian Statistics Conference, Adelaide, Jul 2012.
  * Workshop leader, *Statistical Forecasting: Principles and Practice*, Swiss Statistical Society, Kandersteg, Jun 2011.
  * Keynote speaker, *Extreme Forecasting*, International Symposium on Forecasting, Hong Kong, Jun 2009.

# Grants

```{r grants}
sumgrants <- grants |>
  pull(Amount) |>
  sum(na.rm = TRUE)
```

I have acquired (in most cases jointly) $`r sprintf("%2.1f", sumgrants/1e6)` million in external research grants since 2000. External research grants over $100,000 are listed below.\vspace*{0.2cm}\enlargethispage*{0.5cm}

```{r grantstable, results='asis'}
grants |>
  filter(Amount > 100000, Type == "Research") |>
  mutate(
    Time = paste0(Start, ifelse(is.na(End), "", paste0("--", End))),
    Entry = paste(People, ". ``", Title, "''. ",
      "\\emph{Funding from ", Source, "}",
      sep = ""
    ),
    Amount = dollars(Amount)
  ) |>
  arrange(Time, desc(Amount)) |>
  select(Time, Entry, Amount) %>%
  baretable(
    align = "llp{13.3cm}r",
    hline.after = c(0, NROW(.)),
    size = "\\fontsize{10}{12}",
    add.to.row = list(
      pos = as.list(seq(NROW(.))),
      command = rep("\\\\[-0.32cm]", NROW(.))
    )
  )
```

\newpage

# Teaching

  * In every year since 2018, student evaluations for "Applied forecasting" have given an average rating for my teaching above 4.8 out of 5.
  * In 1998 and 2020, I received the "Excellence in teaching" award from the Monash Student Association.
  * I have received (with George Athanasopoulos), the 2020 Dean's Award for Innovation in Learning and Teaching, the 2021 Vice-Chancellor's Award for Innovation in Learning and Teaching, and the Australian Awards for University Teaching Citation for Outstanding Contributions to Student Learning.
  * I am author of an innovative textbook with George Athanasopoulos entitled *Forecasting: principles and practice* ([`OTexts.org/fpp3/`](https://OTexts.org/fpp3)) which is available online and free of charge. The website has an average of over 25000 pageviews per day.

# Consulting

  * Since 1986, I have worked with several hundred different clients in Australia, the United States, Saudi Arabia, Israel, India, Russia, Switzerland, and the Netherlands. I have produced `r NROW(reports)` written consulting reports (listed on pages \pageref{consultingstart}--\pageref{consultingend}).
  * Six times I have provided expert witness in litigation cases.

# Advisory boards

  * Member of the Scaling committee, Victorian Tertiary Admissions Centre (1994--). This committee is responsible for producing the ATAR for VCE students.
  * Member of the ATAR Technical Group for the Australasian Conference of Tertiary Admissions Centres (2003--).
  * Member of the Indigenous Statistical and Information Advisory Group for the Australian Institute of Health and Welfare (2017--).
  * Member of the Methodology Advisory Committee for the Australian Bureau of Statistics (2010--2018).

# Conference organization

  * Chair, IIF Workshop on Forecast Reconciliation, 2023.
  * General Chair, International Symposium on Forecasting, 2017.
  * Program Chair, International Symposium on Forecasting, 2012.
  * Program Co-Chair, International Symposium on Forecasting, 2004.

```{r publist}
# Set up vector of all bibtypes
bibtype <- as_tibble(pubs) |> pull(bibtype)
bibtype[names(pubs) %in%  c(
  "hyndman2015new",
  "hyndman2015change",
  "IJFeditorial13",
  "tourismeditorial11",
  "IJFeditorial10b",
  "IJFeditorial10a",
  "IJFeditorial06",
  "IJFeditorial05",
  "Gardner23",
  "freditorial"
)] <- "Editorial"
```

# Books

\refstepcounter{bib}\label{papersstart}

```{r}
#| output: asis
pubs[bibtype == "Book"] |>
  add_bib_section()
```

# PhD thesis

```{r phd}
#| output: asis
pubs[bibtype == "PhdThesis"] |>
  add_bib_section()
```

# Refereed research papers

```{r research-papers}
#| output: asis
# Normal articles excluding editorials
pubs[bibtype == "Article"] |>
  add_bib_section()
```

# Book chapters

```{r book-chapters}
#| output: asis
pubs[bibtype %in% c("InBook", "InCollection")] |>
  add_bib_section()
```

# Papers in refereed conference proceedings

```{r papers-in-proceedings}
#| output: asis
pubs[bibtype == "InProceedings"] |>
  add_bib_section()
```

# Unpublished working papers

```{r working-papers}
#| output: asis
pubs[bibtype %in% c("TechReport", "Unpublished")] |>
  add_bib_section()
```

# Book reviews

```{r book-reviews}
#| output: asis
# Need to adjust bibtype so RefManageR understands what to do
pubs[bibtype == "Review"] |>
  change_bibtype("Article") |>
  add_bib_section()
```

# Editorials and obituaries

```{r editorials}
#| output: asis
# Now the editorials
pubs[bibtype == "Editorial"] |>
  add_bib_section()
```

\refstepcounter{bib}\label{papersend}

# Other papers

```{r other}
#| output: asis
# Other papers not counted above
pubs[bibtype == "Report"]  |>
  change_bibtype("Unpublished") |>
  add_bib_section()
```

# Statistical consulting reports

\refstepcounter{bib}\label{consultingstart}

```{r statistical-consulting}
#| output: asis
reports |>
  add_bib_section(rewrite = FALSE)
```

\refstepcounter{bib}\label{consultingend}

# Software (R packages)

\refstepcounter{bib}\label{packagestart}

```{r r-packages-list}
#| output: asis
# Keep order of R packages as they are already sorted by package name
packages |>
  add_bib_section(sorting = "none")
```

\refstepcounter{bib}\label{packageend}
