---
name: Rob J Hyndman
address: "Department of Econometrics & Business Statistics,\\tabularnewline Monash University, VIC 3800, Australia."
www: robjhyndman.com
phone: +61 3 9905 5141
email: "Rob.Hyndman@monash.edu"
twitter: robjhyndman
github: robjhyndman
date: "`r format(Sys.Date(), '%B %Y')`"
date-format: "MMMM YYYY"
position: FAA, FASSA, BSc (Hons), PhD, AStat
format: cv-pdf
pdf-engine: latexmk
header-includes:
  - \geometry{left=1.5cm,right=1.5cm,top=1.8cm,bottom=1.7cm}
  - \definecolor{headcolor}{HTML}{000088}
---

\titlespacing{\section}{0pt}{1.ex}{0.5ex}
\fontsize{10}{11.5}\sf

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = FALSE
)
library(dplyr)
library(RefManageR)
source("R/add_bib_section.R")
source("R/pretty.R")

# Remove any temporary bib file
if (fs::file_exists("temp.bib")) {
  fs::file_delete("temp.bib")
}

targets::tar_load(c(pubs, rjh, rjh_packages, grants, rjhcites))
```

# Education and qualifications

```{r degrees, results='asis'}
tribble(
  ~Year, ~Degree, ~Institution,
  1988, "B.Sc.(Hons)", "University of Melbourne",
  1992, "Ph.D.", "University of Melbourne",
  2000, "A.Stat.", "Statistical Society of Australia"
) %>%
  baretable()
```

# Current position

```{r employment, results='asis'}
tribble(
  ~Years, ~Position,
  "2003--", "\\textbf{Professor}, Department of Econometrics \\& Business Statistics, Monash University"
) %>%
  baretable()
```

# Fellowships

  * Fellow of the Australian Academy of Science (elected 2021).
  * Fellow of the Academy of the Social Sciences in Australia (elected 2020).
  * Fellow of the International Institute of Forecasters (elected 2021).


# Selected awards and honours

```{r awards, results='asis'}
awards <- tribble(
  ~Year, ~Award,
  2022, "Australian Awards for University Teaching citation for outstanding contributions to student learning",
  2021, "Pitman Medal, Statistical Society of Australia",
  2021, "Vice-Chancellor's Award for Innovation in Learning and Teaching",
  2010, "Dean's Award for Excellence in Innovation and External Collaboration, Monash Business School",
  2008, "Dean's Award for Excellence in Research, Monash Business School",
  2008, "Vice-Chancellor's Award for Postgraduate Supervisor of the Year, Monash University",
  2007, "Moran Medal for Statistical Science, Australian Academy of Science"
) %>%
  baretable()
```

# Editorial boards

```{r positions, results='asis'}
tribble(
  ~Start, ~End, ~Position,
  2023, NA, "\\textbf{Executive Editor}, \\textit{The R Journal}",
  2011, NA_character_, "\\textbf{Editor}, \\textit{Journal of Statistical Software}",
  2005, "2018", "\\textbf{Editor-in-Chief}, \\textit{International Journal of Forecasting}",
  2001, "2004, 2019--", "\\textbf{Associate Editor}, \\textit{International Journal of Forecasting}",
  2001, "2004", "\\textbf{Theory and Methods Editor}, \\emph{Australian \\& New Zealand Journal of Statistics}",
) %>%
  mutate(
    Start = as.character(Start),
    End = tidyr::replace_na(End, ""),
    Year = paste(Start, "--", End, sep = "")
  ) %>%
  select(Year, Position) %>%
  baretable()
```

# Research grants

```{r grants}
sumgrants <- grants %>%
  pull(Amount) %>%
  sum(na.rm = TRUE)
```

I have acquired (in most cases jointly) about $`r round(sumgrants/1e6)` million in external research grants since 2000, including 3 ARC Discovery Grants, 3 ARC Linkage Grants, 1 NHMRC Grant, an ARC Centre of Excellence, an ARC Industrial Training Transformation Centre, and contract research grants from many government and business organizations.

# Selected public lectures

  * Belz lecture, *Forecasting and the importance of being uncertain*, Statistical Society Australia, Melbourne, Oct 2006.
  * Knibbs lecture, *Population forecasting and the importance of being uncertain*, Statistical Society Australia, Canberra, Nov 2007.
  * Yahoo Big Thinkers lecture, *Exploring the boundaries of predictability: what can we forecast, and when should we give up?*, California, Jun 2015.
  * Cornish lecture, *Feasts and fables: modern tools for time series analysis*, Adelaide, November 2021.

\enlargethispage*{0.8cm}

# Selected keynote addresses

  * Keynote speaker, *Extreme Forecasting*, International Symposium on Forecasting, Hong Kong, Jun 2009.
  * Keynote speaker, *Man vs Wild Data*, Young Statisticians Conference, Melbourne, Feb 2013.
  * Keynote speaker, *Forecasting without forecasters*, International Symposium on Forecasting, Seoul, Jun 2013.
  * Keynote speaker, *Automatic time series forecasting*, "New Trends on Intelligent Systems and Soft Computing 2014", Granada, Spain, Feb 2014.
  * Keynote speaker, *Forecasting big time series data using R*, Chinese R conference, Nanchang, Oct 2015.
  * Keynote speaker, *Forecasting large collections of related time series*, German Statistical Week, Augsburg, Sep 2016.
  * Keynote speaker, *Visualizing and forecasting big time series data*, ICML Time Series Workshop, Sydney, Aug 2017.
  * Keynote speaker, Beijing Workshop on Forecasting, Nov 2017.
  * Keynote speaker, *10 years of forecast reconciliation*, International Symposium on Forecasting, Oct 2020.
  * Blakers lecture, *Forecasting the future and the future of forecasting*, ANU-AAMT National Mathematics Summer School, January 2022.

# R packages

I have coauthored `r NROW(rjh_packages)` R packages as a result of my research. There have been over `r round(sum(rjh_packages$downloads, na.rm=TRUE)/1e6)` million downloads of my packages since 2015 (to `r format(Sys.time(), "%e %B %Y")`).

# Selected books

```{r books}
#| output: asis
pubs[c("fpp3", "MWH3", "expsmooth08")] |>
  add_bib_section(show_cites = TRUE, rjhcites = rjhcites)
```

\enlargethispage*{1cm}


```{r}
# Count papers
npapers <- pubs %>%
  as_tibble() |>
  filter(!(type %in% c("book", "thesis", "review"))) %>%
  NROW()
```

# Selected papers

Since 1991 I have authored `r npapers` research papers or book chapters on statistical topics. Some highlights are listed below, with citations taken from Google Scholar on `r format(Sys.time(), "%e %B %Y")`.  My h-index is `r rjh$All[2]` with total citations of `r prettyNum(rjh$All[1], big.mark=",")`.


```{r bibfile}
#| output: asis
pubs[c(
    "tsibble", "globalforecasting", "stray", "fforma",
    "forecastsofa", "baggedETS",
    "smartmeterhts", "mint", "HF10", "DHS11", "hierarchical",
    "VHNC10", "HK06", "HK08", "HKSG02", "HF96", "m3pca",
    "ijf25", "HU07", "HDR96",
    "HBG96", "HB08", "tscv"
  )] |>
  add_bib_section(show_cites = TRUE, rjhcites = rjhcites)
```
