---
name: Rob J Hyndman\small\hspace*{0.2cm} FAA, FASSA
address: "Department of Econometrics & Business Statistics,\\tabularnewline Monash University, VIC 3800, Australia."
www: robjhyndman.com
phone: +61 3 9905 5141
email: "Rob.Hyndman@monash.edu"
twitter: robjhyndman
github: robjhyndman
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "000088"
csl: numeric-apa-cv.csl
output:
  vitae::hyndman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE)
library(tidyverse)
library(vitae)
library(gcite)
library(RefManageR)
library(fuzzyjoin)
source("functions.R")

# Update list of R packages I've coauthored
source("R_packages.R")

# Read any bib files
pubs <- bibliography_entries("rjhpubs.bib")
reports <- bibliography_entries("rjhreports.bib")
packages <- bibliography_entries("Rpackages.bib")

# Read grants file
grants <- read_csv("Grant_income.csv")
```

# Education and qualifications

```{r degrees, results='asis'}
tribble(
    ~Degree, ~Institution, ~Year,
    "B.Sc.(Hons)", "University of Melbourne", 1988,
    "Ph.D.", "University of Melbourne", 1992,
    "A.Stat.", "Statistical Society of Australia", 2000
  ) %>%
  baretable()
```

# Current positions

```{r employment, results='asis'}
tribble(
    ~Start, ~End, ~Position,
    2003, NA, "\\textbf{Professor}, Department of Econometrics \\& Business Statistics, Monash University",
    2019, NA, "\\textbf{Head}, Department of Econometrics \\& Business Statistics, Monash University",
  ) %>%
  arrange(-Start) %>%
  mutate(End = replace_na(End, "")) %>%
  mutate(Years = if_else(End == Start,
        as.character(Start),
        paste(Start, "--", End, sep = ""),
        paste(Start, "--", End, sep = ""))) %>%
  select(Years, Position) %>%
  baretable()
```

# Selected awards and honours

```{r awards, results='asis'}
awards <- tribble(
  ~Year, ~Award,
  2021, "Pitman Medal, Statistical Society of Australia",
  2021, "Elected Fellow of the Australian Academy of Science",
  2021, "Elected Fellow of the International Institute of Forecasters",
  2020, "Elected Fellow of the Academy of the Social Sciences in Australia",
  2020, "MSA Teaching Excellence Award for Business and Economics, Monash Student Association",
  2020, "Dean's Award for Innovation in Learning and Teaching, Monash Business School",
  2010, "Dean's Award for Excellence in Innovation and External Collaboration, Monash Business School",
  2010, "HP Innovation Research Award",
  2008, "Dean's award for Excellence in Research, Monash Business School",
  2008, "Vice-Chancellor's award for postgraduate supervisor of the year, Monash University",
  2007, "Moran Medal for Statistical Science, Australian Academy of Science",
  2005, "Elected member of the International Statistical Institute",
) %>%
  baretable()
```

# Teaching and mentoring

  * In each year since 2018, student evaluations for "Applied forecasting for business and economics" gave an average rating for my teaching above 4.8 out of 5.
  * I currently supervise five PhD students and two post-doctoral research fellows. I have previously supervised another 27 PhD students and 3 Masters students.
  * I am author of an innovative textbook with George Athanasopoulos entitled *Forecasting: principles and practice* ([`OTexts.org/fpp3/`](https://OTexts.org/fpp3)) which is available online and free of charge. The website has an average of over 20000 pageviews per day.
  * I publish the [*Hyndsight*](https://robjhyndman.com/hyndsight) blog on research issues which receives an average of about 2000 pageviews per day.

# Editorial boards

```{r positions, results='asis'}
tribble(
  ~Start, ~End, ~Position,
  2011, NA, "\\textbf{Editor}, \\textit{Journal of Statistical Software}",
  2001, 2004, "\\textbf{Associate Editor}, \\textit{International Journal of Forecasting}",
  2019, NA, "\\textbf{Associate Editor}, \\textit{International Journal of Forecasting}",
  2005, 2018, "\\textbf{Editor-in-Chief}, \\textit{International Journal of Forecasting}",
  2001, 2004, "\\textbf{Theory and Methods Editor}, \\emph{Australian \\& New Zealand Journal of Statistics}",
  1996, 2001, "\\textbf{Book Review Editor}, \\emph{Australian Journal of Statistics}",
) %>%
  mutate(End = replace_na(End, "")) %>%
  mutate(Year = paste(Start, "--", End, sep = "")) %>%
  select(Year, Position) %>%
  baretable()
```


# Society leadership

  * Member, Pearson Prize Committee, International Statistical Institute, 2017.
  * Director, International Institute of Forecasters, 2005--2018.
  * Member, Scientific Program Advisory Group, Statistical Society of Australia, 2001--2004
  * Secretary, Victorian branch, Statistical Society of Australia, 1993--1995.
  * Central Council member, Statistical Society of Australia, 1993--1996.


# Research Grants

```{r grants}
grants <- read_csv("Grant_income.csv")
sumgrants <- grants %>%
  pull(Amount) %>%
  sum(na.rm=TRUE)
```

I have acquired (in most cases jointly) about $`r sprintf("%2.1f", sumgrants/1e6)` million in external research grants since 2000. Highlights include being CI on an ARC Centre of Excellence, CI on an ARC Industrial Transformation Training Centre, CI on 3 ARC Discovery Grants, CI on 3 ARC Linkage Grants, and CI on 1 NHMRC grant.

# Selected public and keynote addresses

  * Belz lecture, *Forecasting and the importance of being uncertain*, Statistical Society of Australia, Melbourne, Oct 2006.
  * Knibbs lecture, *Population forecasting and the importance of being uncertain*, Statistical Society of Australia, Canberra, Nov 2007.
  * Invited speaker, *Forecasting functional time series*, Australian Frontiers of Science, Canberra, Feb 2008.
  * Keynote speaker, *Extreme Forecasting*, International Symposium on Forecasting, Hong Kong, Jun 2009.
  * Keynote speaker, *Man vs Wild Data*, Young Statisticians Conference, Melbourne, Feb 2013.
  * Keynote speaker, *Forecasting without forecasters*, International Symposium on Forecasting, Seoul, Jun 2013.
  * Keynote speaker, *Automatic time series forecasting*, "New Trends on Intelligent Systems and Soft Computing 2014", Granada, Spain, Feb 2014.
  * Keynote speaker, *Challenges in forecasting peak electricity demand*, Energy Forum, Valais, Switzerland, Jun 2014.
  * Yahoo Big Thinkers lecture, *Exploring the boundaries of predictability: what can we forecast, and when should we give up?*, California, Jun 2015.
  * Keynote speaker, *Forecasting big time series data using R*, Chinese R conference, Nanchang, Oct 2015.
  * Keynote speaker, *Forecasting large collections of related time series*, German Statistical Week, Augsburg, Sep 2016.
  * Keynote speaker, *Visualizing and forecasting big time series data*, ICML Time Series Workshop, Sydney, Aug 2017.
  * Keynote speaker, Beijing Workshop on Forecasting, Nov 2017.
  * Keynote speaker, *10 years of forecast reconciliation*, International Symposium on Forecasting, Oct 2020.
  * ACEMS public address, *Uncertain futures: what can we forecast and when should we give up?*, Aug 2021.

# Advisory boards

  * Member of the Scaling committee, Victorian Tertiary Admissions Centre (1994--). This committee is responsible for producing the ATAR for VCE students.
  * Member of the ATAR Technical Group for the Australasian Conference of Tertiary Admissions Centres (2003--).
  * Member of the Indigenous Statistical and Information Advisory Group for the Australian Institute of Health and Welfare (2017--).
  * Member of the Methodology Advisory Committee for the Australian Bureau of Statistics (2010--2018).

# Conference organization

  * General Chair, International Symposium on Forecasting, 2017
  * Program Chair, International Symposium on Forecasting, 2012.
  * Program Co-Chair, International Symposium on Forecasting, 2004.

# R packages

I have coauthored `r NROW(rjhpackages)` R packages as a result of my research. There have been over `r round(sum(rjhpackages$count, na.rm=TRUE)/1e6)` million downloads of my packages since 2015 (to `r format(Sys.time(), "%e %B %Y")`).

# Selected books

```{r books}
pubs %>%
  filter(type == "book") %>%
  filter(id %in% c("fpp3","MWH3","expsmooth08")) %>%
  arrange(issued, author$family)
```

# Research

* Since 1991 I have authored `r NROW(pubs)` papers, chapters or books on statistical topics. A selection of these are listed below.
* I have an h-index of 66 on Google Scholar, with 39,700 citations of my papers.

# Selected research papers

```{r best}
pubs %>%
  filter(id %in% c("gravitas","uslongevity","smartmeterhts","mint","HF10","DHS11","hierarchical","lhf","dobin","forecastingcompetitions","forecastingsofa",
         "VHNC10","HK06","HK08","HKSG02","HF96","stray","oddstream",
         "ijf25","HU07","HDR96","gefcom2014","swissexports",
         "HBG96","HB08","tscv","temporal-hierarchies")
  ) %>%
  mutate(year = as.numeric(unlist(issued))) %>%
  arrange(-year)
```

