---
name: Rob J Hyndman
address: "Department of Econometrics & Business Statistics,\\tabularnewline Monash University, VIC 3800, Australia."
www: robjhyndman.com
phone: +61 3 9905 5141
email: "Rob.Hyndman@monash.edu"
twitter: robjhyndman
github: robjhyndman
date: "`r format(Sys.time(), '%B %Y')`"
position: FAA, FASSA, BSc (Hons), PhD, AStat
csl: numeric-apa-cv.csl
output: vitae::hyndman
header-includes:
  - \geometry{left=1.5cm,right=1.5cm,top=1.8cm,bottom=1.7cm}
  - \definecolor{headcolor}{HTML}{000088}
editor_options: 
  chunk_output_type: console
---

\titlespacing{\section}{0pt}{1.ex}{0.5ex}
\fontsize{10}{11.5}\sf
\thispagestyle{empty}
\enlargethispage*{0.5cm}

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = FALSE
)
library(tidyverse)
library(RefManageR)
library(vitae)
library(gcite)
library(fuzzyjoin)
source("functions.R")
source("gscholar.R")

# Update list of R packages I've coauthored
rjh_packages <- get_rjh_packages()

# Read any bib files
pubs <- bibliography_entries("rjhpubs.bib") |>
    mutate(year = lubridate::year(as.Date(issued)))
reports <- bibliography_entries("rjhreports.bib")
packages <- bibliography_entries("Rpackages.bib")

# Read grants file
grants <- read_csv("Grant_income.csv")
```

# Current position

```{r employment, results='asis'}
tribble(
  ~Start, ~End, ~Position,
  2003, NA, "\\textbf{Professor}, Department of Econometrics \\& Business Statistics, Monash University"
) %>%
  arrange(-Start) %>%
  mutate(
    Start = as.character(Start),
    End = as.character(End),
    End = replace_na(End, ""),
    Years = if_else(End == Start,
        as.character(Start),
        paste(Start, "--", End, sep = ""),
        paste(Start, "--", End, sep = "")
    )
  ) |>
  select(Years, Position) |>
  baretable()
```

# Fellowships

  * Fellow of the Australian Academy of Science (elected 2021).
  * Fellow of the Academy of the Social Sciences in Australia (elected 2020).
  * Fellow of the International Institute of Forecasters (elected 2021).

# Selected awards and honours

```{r awards, results='asis'}
awards <- tribble(
  ~Year, ~Award,
  2021, "Pitman Medal, Statistical Society of Australia",
  2007, "Moran Medal for Statistical Science, Australian Academy of Science"
) %>%
  baretable()
```

# Selected books

```{r books}
pubs %>%
  filter(id %in% c("fpp3","expsmooth08")) %>%
  arrange(issued, author$family)
```

\vspace*{-0.2cm}

# Selected papers

```{r}
# Count papers
npapers <- pubs %>%
  filter(!(type %in% c("book","thesis","review"))) %>%
  NROW()
```

Since 1991 I have authored `r npapers` research papers or book chapters on statistical topics. Some highlights are listed below, with citations taken from Google Scholar on `r format(Sys.time(), "%e %B %Y")`. My h-index is `r rjh$All[2]` with total citations of `r rjh$All[1]`.

```{r bibfile, dependson='GScholar'}
# Add Google scholar citations by fuzzy matching on title
pubs <- pubs %>%
  stringdist_join(
    gspapers %>% select(title, n_citations), 
    by = "title", ignore_case=TRUE
  ) %>%
  rename(title = title.x) %>%
  mutate(note = paste0(". \\emph{[Citations: ", n_citations, "]}.")) |> 
  select(-title.y)

# Show selected publications
pubs %>%
  filter(id %in% c(
    "tsibble","globalforecasting","fforma",
       "smartmeterhts","mint","HF10","DHS11","hierarchical",
         "VHNC10","HK06","HK08","HKSG02","HF96","m3pca",
         "HU07","HDR96",
         "HB08"
  )) %>%
  arrange(-year)
```

