---
name: Rob J Hyndman
address: "Department of Econometrics & Business Statistics, Monash University, VIC 3800, Australia."
twitter: robjhyndman
email: Rob.Hyndman@monash.edu
github: robjhyndman
www: robjhyndman.com
phone: +61 3 9905 5141
date: "`r format(Sys.time(), '%B %Y')`"
bibliography: [rjhpubs.bib, rjhreports.bib, Rpackages.bib]
geometry: "left=1.75cm,right=1.75cm,top=2.2cm,bottom=2.2cm"
output:
  bookdown::pdf_document2:
    template: rjhcv.tex
    keep_tex: yes
---

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(fontawesome)
library(pander)
opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
baretable <- function(tbl, digits=0, ...) {
  tbl %>%
	  xtable::xtable(digits=digits) %>%
    print(include.colnames=FALSE,
  	      include.rownames=FALSE,
  	      hline.after=NULL,
  	      comment=FALSE,
  	      latex.environments=NULL,
          floating=FALSE,
          sanitize.text.function = function(x) {x})
}
```

# Education and qualifications

```{r degrees, results='asis'}
tribble(
    ~Year , ~Degree       , ~Institution                       ,
    1998 , "B.Sc.(Hons)" , "University of Melbourne"          ,
    1992 , "Ph.D."       , "University of Melbourne"          ,
    2000 , "A.Stat."     , "Statistical Society of Australia"
  ) %>%
  baretable()
```

# Recent and current positions

\begin{tabular}{lP{15cm}}
2019--&
  \textbf{Head},
  Department of Econometrics \& Business Statistics, Monash University.\\
2011--&
  \textbf{Editor},
  \textit{Journal of Statistical Software}. \\
2005--2018 &
  \textbf{Editor-in-Chief},
  \textit{International Journal of Forecasting}.\\
2005--2018 &
  \textbf{Director},
  International Institute of Forecasters.\\
2003--&
  \textbf{Professor of Statistics},
  Department of Econometrics \& Business Statistics, Monash University.
\end{tabular}


# Honours and awards

\begin{tabular}{ll}
2016 & KNAW Visiting Professor, TU/Eindhoven, Netherlands.\\
2010 & Dean's Award for excellence in innovation and external collaboration, Monash University.\\
2010 & HP Innovation Research Award.\\
%2009--2010 & Entry in \emph{Great minds of the 21st century}, 1st--4th editions.\\
2008 & Dean's award for excellence in research, Monash University.\\
2008 & Vice-Chancellor's award for postgraduate supervisor of the year, Monash University.\\
2007 & Knibbs Lecturer, Statistical Society of Australia (ACT branch).\\
2007 & Moran Medal for Statistical Science, Australian Academy of Science.\\
2006 & Belz Lecturer, Statistical Society of Australia (Victorian branch).\\
%2003 & Entry in \textit{One thousand great intellectuals}, 1st edition.\\
%2002-- & Entry in \textit{Who's Who in Finance and Business}, from 33rd edition.\\
%2001--2008 & Entry in \textit{2000 Outstanding Intellectuals of the 21st Century}, 1st--5th editions.\\
%2001--2003 & Entry in \textit{International Directory of Distinguished Leadership}, 9th--11th editions.\\
%2001-- & Entry in \textit{Who's Who in Science and Engineering}, from 6th edition.\\
%2001 & Entry in \textit{Who's Who in the 21st Century}, 1st edition.\\
%2000 & Entry in \textit{Outstanding People of the 20th Century}, 2nd edition.\\
%2000-- & Entry in \textit{Cambridge Dictionary of International Biography}, from 28th edition.\\
%2000-- & Entry in \textit{Who's Who in Asia and the Pacific Nations}, from 4th edition.\\
%1998-- & Entry in Marquis \textit{Who's Who in the World}, from 15th edition.\\
1998 & Award for excellence in teaching, Monash Science Society\\
%1997 & Citation of excellence by ANBAR for Hyndman (1995)\\
1990 & Finalist, Channel Ten Young Achiever Awards\\
1988 & Dwights Prize in Statistics, University of Melbourne\\
%1988 & First Class Science Faculty Honours, University of Melbourne\\
1987 & Norma McArthur Prize in Statistics, University of Melbourne\\
%1987 & First Class Science Faculty Honours, University of Melbourne\\
1986 & Second Maurice H.\ Belz Prize in Statistics, University of Melbourne
\end{tabular}

# Membership of associations

\begin{tabular}{@{~$\bullet$~~}l}
Elected Member, International Statistical Institute.\\
Member, International Institute of Forecasters.\\
Member, International Association for Statistical Computing.\\
Member, Statistical Society of Australia.
\end{tabular}

# Research

 * Since 1991 I have authored \ref{sumpapers} papers, chapters or books on statistical topics. A list of these appears on pages \pageref{papersstart}--\pageref{papersend}.
 * My current research involves the analysis of large collections of time series, and includes visualization, forecasting, reconciliation and modelling. Applications include electricity demand and smart-meter data, security sensors, manufacturing data and retail sales.
 * I currently supervise six PhD students and two post-doctoral research fellows. I have previously supervised another 22 PhD students and 3 Masters students.
 * I publish the [*Hyndsight*](https://robjhyndman.com/hyndsight) blog on research issues which receives an average of about 2000 pageviews per day.
 * I have produced \ref{sumsoftware} R packages as a result of my research. These are listed on pages~\pageref{sumreports}--\pageref{sumsoftware}.

# Grants

I have acquired (in most cases jointly) about $5 million in external research grants since 2000. External research grants over $20,000 are listed below.

{\def\next{\\\\[-0.2cm]}\fontsize{10}{12pt}\selectfont
\begin{tabular}{@{}lP{13.3cm}r@{}}
\toprule
2000 & R.J. Hyndman. ``Forecasting Telstra market share''. \emph{Funding from Telstra Australia.} &\$31,000
\next
2000 & R.J. Hyndman. ``Electricity demand forecasting''. \emph{Funding from TXU.} & \$27,933
\next
2001--2002 & R.J. Hyndman. ``Injury management pilot evaluation''. \emph{Funding from Workcover NSW.} &\$42,182
\next
2002 & R.J. Hyndman. ``Evaluation of PBS Forward Estimates methodology''. \emph{Funding from Department of Health and Ageing.} &\$55,341
\next
2004--2008 & R.J. Hyndman. ``Analysis of NPS interventions''. \emph{Funding from the National Prescribing Service.} &\$120,000
\next
2004--2006 & G.M. Martin, R.D. Snyder and R.J. Hyndman. ``New approaches to the analysis of count time series''. \emph{Funding from the Australian Research Council.} &\$172,317
\next
2006--2010 & R.J. Hyndman and G. Athanasopoulos. ``Tourism Forecasting''. \emph{Funding from Tourism Australia and the Sustainable Tourism Cooperative Research Centre.} &\$312,017
\next
2007--2010 & R.J. Hyndman, ``Peak energy demand forecasting''. \emph{Funding from the Electricity Supply Industry Planning Council, Victorian Energy Corporation, Western Power and the Australian Energy Market Operator.} &\$606,995
\next
2008 & R.J. Hyndman. ``PBS Forecasting Model Review''. \emph{Funding from the Commonwealth Department of Health and Ageing.} &\$46,514
\next
2009--2011 & Erbas, B., Abramson, M., Tang, M., Allen, K., Newbigin, E., Dharmage, S., Hyndman, R.J. ``The impact of outdoor aeroallergen exposure on asthma exacerbations in children and adolescents''. \emph{Funding from the National Health and Medical Research Council.} &\$454,550
\next
2010--2011 & R.J. Hyndman. ``New methods for hierarchical forecasting with application to HP business forecasting''. \emph{Funding from the HP Labs Innovation Research Program}. &US\$27,800
\next
2011--2015 & R.J. Hyndman, ``Energy demand forecasting''. \emph{Funding from the Australian Energy Market Operator.} &\$1,106,900
\next
2011--2013 & R.J. Hyndman and S. Fan, ``Development of electricity peak demand and energy forecasts for the SWIS''. \emph{Funding from the Independent Market Operator (Western Australia)}. &\$93,450
\next
2013--2016 & K.A. Smith-Miles, R.J. Hyndman, L. Villanova and M. Kah. ``Optimising experimental design for robust product development: a cast study for high-efficiency energy generation''. \emph{ARC Linkage Grant with Ceramic Fuel Cells Ltd}. & \$362,389
\next
2014--2017 & A.N. Panagiotelis, G. Athanasopoulos, R.J. Hyndman, F. Vahid. ``Macroeconomic forecasting in a `Big Data' world''. \emph{ARC Discovery Grant}.& \$451,034
\next
2017--2018 & R.J. Hyndman, S. Ben Taieb, C. Bergmeir. ``Demand forecasting for large-scale dynamic hierarchies in a big data environment'' \emph{Funding from Huawei Innovation Research Program} & \$86,586
\next
2017--2019&  R.J. Hyndman, D. Cook, P. Toscas. ``RiskLab Projects: Econometrics''. \emph{RiskLab at Data61}. & \$151,200
\next
2017--2019 & K.A. Smith-Miles, R.J. Hyndman, M. Munoz Acosta, J. Katsifolis. ``Intruder Alert! Detecting and classifying events in noisy time series''. \emph{ARC Linkage Grant}. & \$204,000
\next
2017--2021 & Hall, P., Bartlett, P., Bean, N., Burrage, K., DeGier, J., Delaigle, A., Forrester, P., Geweke, J., Kohn, R., Kroese, D., Mengersen, K., Pettit, A., Pollett, P., Roughan, M., Ryan, L., Taylor, P., Turner, I., Wand, M., Garoni, T., Smith-Miles, K. A., Caley, M., Churches, T., Elazar, D., Gupta, A., Harch, B., Tam, S., Weegberg, K., Willinger, W. \& Hyndman, R.J. \emph{ARC Centre of Excellence for Mathematical and Statistical Frontiers} & \$554,329
\\
\bottomrule
\end{tabular}}
