---
name: Rob J Hyndman
address: "Department of Econometrics & Business Statistics, Monash University, VIC 3800, Australia."
twitter: robjhyndman
email: Rob.Hyndman@monash.edu
github: robjhyndman
www: robjhyndman.com
phone: +61 3 9905 5141
date: "`r format(Sys.time(), '%B %Y')`"
bibliography: [rjhpubs.bib, rjhreports.bib, Rpackages.bib]
geometry: "left=1.75cm,right=1.75cm,top=2.2cm,bottom=2.2cm"
output:
  bookdown::pdf_document2:
    template: rjhcv.tex
    keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(RefManageR)
rjh <- ReadBib("rjhpubs.bib", check=FALSE)
types <- as_tibble(rjh) %>% pull(bibtype)
books <- paste(unlist(rjh[types=="Book"]$key),sep="")
papers <- paste(unlist(rjh[types=="Article"]$key),sep="")
baretable <- function(tbl, digits=0, ...) {
  tbl %>%
	  xtable::xtable(digits=digits) %>%
    print(include.colnames=FALSE,
  	      include.rownames=FALSE,
  	      hline.after=NULL,
  	      comment=FALSE,
  	      latex.environments=NULL,
          floating=FALSE,
          sanitize.text.function = function(x) {x})
}
printbibliography <- function(
			categories=c("Book","Article"),
			titles=c("Books","Refereed journal papers")) {
	cat1 <- paste(unlist(rjh[types==categories[1]]$key),sep="")
	cat(paste("\\defbibheading{cat1}{\\section*{",titles[1],"}}",sep=""))
  cat(paste("\\addtocategory{cat1}{",paste(cat1,",",sep="",collapse=""),"}",sep=""))
	cat("\\begin{publications}")
	cat("\\printbib{cat1}",sep="")
	cat("\\end{publications}")
}
```

# Education and qualifications

```{r degrees, results='asis'}
tribble(
    ~Year , ~Degree       , ~Institution                       ,
    1998 , "B.Sc.(Hons)" , "University of Melbourne"          ,
    1992 , "Ph.D."       , "University of Melbourne"          ,
    2000 , "A.Stat."     , "Statistical Society of Australia"
  ) %>%
  baretable()
```

# Recent and current positions

\begin{tabular}{lP{15cm}}
2019--&
  \textbf{Head},
  Department of Econometrics \& Business Statistics, Monash University.\\
2011--&
  \textbf{Editor},
  \textit{Journal of Statistical Software}. \\
2005--2018 &
  \textbf{Editor-in-Chief},
  \textit{International Journal of Forecasting}.\\
2005--2018 &
  \textbf{Director},
  International Institute of Forecasters.\\
2003--&
  \textbf{Professor of Statistics},
  Department of Econometrics \& Business Statistics, Monash University.
\end{tabular}


# Honours and awards

\begin{tabular}{ll}
2016 & KNAW Visiting Professor, TU/Eindhoven, Netherlands.\\
2010 & Dean's Award for excellence in innovation and external collaboration, Monash University.\\
2010 & HP Innovation Research Award.\\
2008 & Dean's award for excellence in research, Monash University.\\
2008 & Vice-Chancellor's award for postgraduate supervisor of the year, Monash University.\\
2007 & Knibbs Lecturer, Statistical Society of Australia (ACT branch).\\
2007 & Moran Medal for Statistical Science, Australian Academy of Science.\\
2006 & Belz Lecturer, Statistical Society of Australia (Victorian branch).\\
1998 & Award for excellence in teaching, Monash Science Society\\
1990 & Finalist, Channel Ten Young Achiever Awards\\
1988 & Dwights Prize in Statistics, University of Melbourne\\
1987 & Norma McArthur Prize in Statistics, University of Melbourne\\
1986 & Second Maurice H.\ Belz Prize in Statistics, University of Melbourne
\end{tabular}

# Membership of associations

\begin{tabular}{@{~$\bullet$~~}l}
Elected Member, International Statistical Institute.\\
Member, International Institute of Forecasters.\\
Member, International Association for Statistical Computing.\\
Member, Statistical Society of Australia.
\end{tabular}

# Research

 * Since 1991 I have authored \ref{sumpapers} papers, chapters or books on statistical topics. A list of these appears on pages \pageref{papersstart}--\pageref{papersend}.
 * My current research involves the analysis of large collections of time series, and includes visualization, forecasting, reconciliation and modelling. Applications include electricity demand and smart-meter data, security sensors, manufacturing data and retail sales.
 * I currently supervise six PhD students and two post-doctoral research fellows. I have previously supervised another 22 PhD students and 3 Masters students.
 * I publish the [*Hyndsight*](https://robjhyndman.com/hyndsight) blog on research issues which receives an average of about 2000 pageviews per day.
 * I have produced \ref{sumsoftware} R packages as a result of my research. These are listed on pages~\pageref{sumreports}--\pageref{sumsoftware}.

# Grants

I have acquired (in most cases jointly) about $5 million in external research grants since 2000. External research grants over $20,000 are listed below.

\def\next{\\\\[-0.2cm]}
\begin{tabular}{@{}lP{13.3cm}r@{}}
\toprule
2000 & R.J. Hyndman. ``Forecasting Telstra market share''. \emph{Funding from Telstra Australia.} &\$31,000
\next
2000 & R.J. Hyndman. ``Electricity demand forecasting''. \emph{Funding from TXU.} & \$27,933
\next
2001--2002 & R.J. Hyndman. ``Injury management pilot evaluation''. \emph{Funding from Workcover NSW.} &\$42,182
\next
2002 & R.J. Hyndman. ``Evaluation of PBS Forward Estimates methodology''. \emph{Funding from Department of Health and Ageing.} &\$55,341
\next
2004--2008 & R.J. Hyndman. ``Analysis of NPS interventions''. \emph{Funding from the National Prescribing Service.} &\$120,000
\next
2004--2006 & G.M. Martin, R.D. Snyder and R.J. Hyndman. ``New approaches to the analysis of count time series''. \emph{Funding from the Australian Research Council.} &\$172,317
\next
2006--2010 & R.J. Hyndman and G. Athanasopoulos. ``Tourism Forecasting''. \emph{Funding from Tourism Australia and the Sustainable Tourism Cooperative Research Centre.} &\$312,017
\next
2007--2010 & R.J. Hyndman, ``Peak energy demand forecasting''. \emph{Funding from the Electricity Supply Industry Planning Council, Victorian Energy Corporation, Western Power and the Australian Energy Market Operator.} &\$606,995
\next
2008 & R.J. Hyndman. ``PBS Forecasting Model Review''. \emph{Funding from the Commonwealth Department of Health and Ageing.} &\$46,514
\next
2009--2011 & Erbas, B., Abramson, M., Tang, M., Allen, K., Newbigin, E., Dharmage, S., Hyndman, R.J. ``The impact of outdoor aeroallergen exposure on asthma exacerbations in children and adolescents''. \emph{Funding from the National Health and Medical Research Council.} &\$454,550
\next
2010--2011 & R.J. Hyndman. ``New methods for hierarchical forecasting with application to HP business forecasting''. *Funding from the HP Labs Innovation Research Program*. &US\$27,800
\next
2011--2015 & R.J. Hyndman, ``Energy demand forecasting''. \emph{Funding from the Australian Energy Market Operator.} &\$1,106,900
\next
2011--2013 & R.J. Hyndman and S. Fan, ``Development of electricity peak demand and energy forecasts for the SWIS''. \emph{Funding from the Independent Market Operator (Western Australia)}. &\$93,450
\next
2013--2016 & K.A. Smith-Miles, R.J. Hyndman, L. Villanova and M. Kah. ``Optimising experimental design for robust product development: a cast study for high-efficiency energy generation''. *ARC Linkage Grant with Ceramic Fuel Cells Ltd*. & \$362,389
\next
2014--2017 & A.N. Panagiotelis, G. Athanasopoulos, R.J. Hyndman, F. Vahid. ``Macroeconomic forecasting in a `Big Data' world''. *ARC Discovery Grant*.& \$451,034
\next
2017--2018 & R.J. Hyndman, S. Ben Taieb, C. Bergmeir. ``Demand forecasting for large-scale dynamic hierarchies in a big data environment'' *Funding from Huawei Innovation Research Program* & \$86,586
\next
2017--2019&  R.J. Hyndman, D. Cook, P. Toscas. ``RiskLab Projects: Econometrics''. \emph{RiskLab at Data61}. & \$151,200
\next
2017--2019 & K.A. Smith-Miles, R.J. Hyndman, M. Munoz Acosta, J. Katsifolis. ``Intruder Alert! Detecting and classifying events in noisy time series''. *ARC Linkage Grant*. & \$204,000
\next
2017--2021 & Hall, P., Bartlett, P., Bean, N., Burrage, K., DeGier, J., Delaigle, A., Forrester, P., Geweke, J., Kohn, R., Kroese, D., Mengersen, K., Pettit, A., Pollett, P., Roughan, M., Ryan, L., Taylor, P., Turner, I., Wand, M., Garoni, T., Smith-Miles, K. A., Caley, M., Churches, T., Elazar, D., Gupta, A., Harch, B., Tam, S., Weegberg, K., Willinger, W. \& Hyndman, R.J. *ARC Centre of Excellence for Mathematical and Statistical Frontiers* & \$554,329
\\
\bottomrule
\end{tabular}

# Major invited talks

  * Belz lecture, *Forecasting and the importance of being uncertain*, Statistical Society of Australia, Melbourne, October 2006.
  * Knibbs lecture, *Population forecasting and the importance of being uncertain*, Statistical Society of Australia, Melbourne, November 2007.
  * Invited speaker, *Forecasting functional time series*, Australian Frontiers of Science, Canberra, February 2008.
  * Keynote speaker, *Extreme Forecasting*, International Symposium on Forecasting, Hong Kong, June 2009.
  * Workshop leader, *Statistical Forecasting: Principles and Practice*, Swiss Statistical Society, Kandersteg, June 2011.
  * Invited speaker, *Advances in automatic time series forecasting*, Australian Statistics Conference, Adelaide, July 2012.
  * Keynote speaker, *Man vs Wild Data*, Young Statisticians Conference, Melbourne, February 2013.
  * Keynote speaker, *Forecasting without forecasters*, {International Symposium on Forecasting}, Seoul, June 2013.
  * Keynote speaker, *Automatic time series forecasting*,  ``New Trends on Intelligent Systems and Soft Computing 2014'', University of Granada, Spain, February 2014.
  * Workshop leader, *State space models for time series*, Australian Bureau of Statistics, May 2014.
  * Keynote speaker, *Challenges in forecasting peak electricity demand*, Energy Forum, Valais, Switzerland, June 2014.
  * Workshop leader, *Functional time series in demography*, Humboldt University, Berlin, June 2014.
  * Workshop leader, *Forecasting: principles and practice*, University of Western Australia, September 2014.
  * Invited speaker, *Visualization and forecasting of big time series data*,   ACEMS Big data workshop, QUT, February 2015.
  * Keynote speaker,  *Exploring the boundaries of predictability: what can we forecast, and when should we give up?*, Yahoo Big Thinkers, June 2015.
  * Keynote speaker, *Forecasting big time series data using R*, Chinese R conference, Nanchang, October 2015.
  * Keynote speaker, *Forecasting large collections of related time series*, German Statistical Week, Augsburg, September 2016.
  * Invited speaker, International Symposium on Energy Analytics, Cairns, June 2017.
  * Keynote speaker, ICML Time Series Workshop, Sydney, August 2017.
  * Keynote speaker, Beijing Workshop on Forecasting, November 2017.
  * Workshop leader, *Forecasting: principles and practice*, New York City, June 2018.
  * Monash master class, *Forecasting the future of the power industry: What can you learn from smart meter data?*, Melbourne, September 2018.


# Teaching

  * Student evaluations for the undergraduate subject "Applied forecasting for business and economics" in 2018 rated my teaching at 4.82 out of 5.
  * In 1998, I received the award for "Excellence in teaching" by the Monash Science Society. This is awarded by the students of the Science faculty.
  * I am author of an innovative textbook with George Athanasopoulos entitled *Forecasting: principles and practice* ([`OTexts.org/fpp2/`](https://OTexts.org/fpp2)) which is available online and free of charge. The website has an average of 11400 pageviews per day.

# Consulting

  * Since 1986, I have worked with several hundred different clients in Australia, the United States, Saudi Arabia, Israel, India, Russia, Switzerland, and the Netherlands. I have produced \ref{sumreports} written consulting reports, listed on pages~\pageref{consulting}--\pageref{sumreports}.
  * Six times I have provided expert witness in litigation cases.

# Advisory boards

  * Member of the Scaling committee, Victorian Tertiary Admissions Centre. This committee is responsible for producing the ATAR for VCE students.
  * Member of the Interstate Transfer Index Technical Group for the Australasian Conference of Tertiary Admissions Centres.
  * Member of the Aboriginal and Torres Strait Islander Statistical and Technical Advisory Group for the Australian Institute of Health and Welfare.
  * Member of the Methodology Advisory Committee for the Australian Bureau of Statistics.


# Publications

```{r, results='asis'}
printbibliography()
```


