---
name: Rob J Hyndman
address: "Department of Econometrics & Business Statistics,
Monash University, VIC 3800, Australia."
twitter: "@robjhyndman"
email: Rob.Hyndman@monash.edu
github: robjhyndman
www: robjhyndman.com
phone: +61 3 9905 5141
date: "`r format(Sys.time(), '%B %Y')`"
bibliography: [rjhpubs.bib, rjhreports.bib, Rpackages.bib]
output:
  bookdown::pdf_document2:
    template: rjhcv.tex
---

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(huxtable)
library(fontawesome)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = 'figure/', cache.path = 'cache/', fig.align = 'center',
  fig.width = 12, fig.height = 4, fig.show = 'hold',
  cache = TRUE, external = TRUE, dev = 'svglite', dev.args = list(bg = "transparent")
)
baretable <- function(tbl, ...) {
	  tbl %>%
	  xtable::xtable() %>%
    print(include.colnames=FALSE,
  	      include.rownames=FALSE,
  	      hline.after=NULL,
  	      comment=FALSE,
  	      latex.environments=NULL)
}
```

# Education and qualifications

```{r degrees, results='asis'}
tribble(
	  ~Year, ~Degree, ~Institution,
  	1998L, "B.Sc.(Hons)", "University of Melbourne",
  	1992L, "Ph.D.", "University of Melbourne",
  	2000L, "A.Stat.", "Statistical Society of Australia"
  ) %>%
  baretable()
```


# Recent and current positions

```{r positions, results='asis'}
tribble(
		~Years, ~Position,
    "2019", "Head of Department, Department of Econometrics & Business Statistics, Monash University",
    "2003", "Professor of Statistics, Department of Econometrics & Business Statistics, Monash University",
    "2005--2018", "Director, International Institute of Forecasters",
    "2005--2018", "Editor-in-Chief, International Journal of Forecasting",
    "2011", "Editor, *Journal of Statistical Software*"
  ) %>%
  baretable()
```


# Research

 * Since 1991 I have authored \ref{sumpapers} papers, chapters or books on statistical topics. A list of these appears on pages \pageref{papersstart}--\pageref{papersend}.
 * My current research involves the analysis of large collections of time series, and includes visualization, forecasting, reconciliation and modelling. Applications include electricity demand and smart-meter data, security sensors, manufacturing data and retail sales.
 * I currently supervise six PhD students and two post-doctoral research fellows. I have previously supervised another 22 PhD students and 3 Masters students.
 * I publish a blog on research issues [robjhyndman.com/hyndsight/](https://robjhyndman.com/hyndsight/) which receives an average of about 2000 pageviews per day.
 * I have produced \ref{sumsoftware} R packages as a result of my research. These are listed on pages~\pageref{sumreports}--\pageref{sumsoftware}.
